---
title: "Codebook Data cleaning project"
author: "J.R. Westerink"
date: "31 mei 2016"
output: 
  html_document:
   keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Project description
During this project a clean, tidy dataset was created from the following source
http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones

# Data processing
runAnalysis.R processes the following files:

* UCI HAR Dataset/activity_labels.txt     
* UCI HAR Dataset/features.txt           
* UCI HAR Dataset/test/subject_test.txt   
* UCI HAR Dataset/test/X_test.txt        
* UCI HAR Dataset/test/y_test.txt         
* UCI HAR Dataset/train/subject_train.txt
* UCI HAR Dataset/train/X_train.txt       
* UCI HAR Dataset/train/y_train.txt 

# Creating the tidy data
The tidy data can be created by running runAnalysis.R, which takes care of downloading and processing the raw data.


# Description of the values in the tidy dataset
```{r echo=FALSE, comment=NA, collapse = TRUE}
tidy <- read.csv("tidy.csv")

cat("Dimensions of the tidy dataset (rows,columns):")
print(dim(tidy))
cat("Variables in the tidy dataset:")
print(names(tidy))
 ```


## activityId
The activityId is the unique identifier for the activity that took place. Also see activityDescription
```{r echo=FALSE, comment=NA, collapse = TRUE, results="markup"}
cat("Values:")
print(unique(tidy$activityId))
```


## activityDescription
The activityDescription contains information about the activity that took place.
```{r echo=FALSE, comment=NA, collapse = TRUE}
cat("Values:")
print(levels(tidy$activityDescription))
```

## subjectId
The subjectId is the unique identifier for the subject that participated in the experiment.
```{r echo=FALSE, comment=NA, collapse = TRUE}
cat("Values:")
print(unique(tidy$subjectId))
```

## Sensor
The sensor variable contains information about the sensor that took the measurement.
```{r echo=FALSE, comment=NA, collapse = TRUE}
cat("Values:")
print(levels(tidy$Sensor))
```

## Average
The Average variable contains the average of the measurement per person, activity and sensor.
The unit of the measures varies depending on the sensor type.




